\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in, paperheight=11.5in]{geometry} % Document margins% Document margins

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Valentyn Yukhymenko} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+380975706703 \\ \href{mailto:balik.work@gmail.com}{balik.work@gmail.com} \\ \href{https://www.linkedin.com/in/balikfromua/}{LinkedIn} \\ \href{https://github.com/BaLiKfromUA}{GitHub}} 
 % Your phone number, email, linkedin, and (optional) website

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Bachelor of  Computer Engineering}, Kharkiv National University of Radioelectronics \hfill {\bf Expected July 2022}\\
Major --— Cybersecurity \hfill {\bf GPA: 3.75/4}
\end{rSection}
\begin{rSection}{Technical Skills}
Java, Python, Golang, JavaScript, C++ (basics), Bash, SQL, Git, Linux, Docker, Spring framework, Vue.js.
\end{rSection}
\begin{rSection}{EXPERIENCE}
\vspace{1mm}
\textbf{Software Engineer Intern} \hfill July 2021 -- September 2021\\
Bloomberg L.P. \hfill \textit{London, UK}\\
\vspace{-3.5mm}
 \begin{itemize}[topsep=2pt, partopsep=0pt, itemsep=7pt,parsep=-5pt]
     \item Built distributed system that integrates post-deployment checks into automated deployment pipeline using Golang, Python, JavaScript, Kafka.
    \item Presented this project at 5 internal events in order to encourage developers to use new integration.
 \end{itemize}

\textbf{Software Engineer} \hfill June 2020 -- May 2021\\
Bookmap \hfill \textit{remote / Ukraine}
 \begin{itemize}[topsep=2pt, itemsep=7pt,parsep=-5pt]
     \item Developed, released and maintained the \href{{https://bookmap.com/knowledgebase/docs/Addons-Multibook}}{Multibook} add-on which led to 50\% increase in monthly paid subscriptions and 35\% increase in annual subscriptions during Q2 2021;
     \item Leaded the migration of the Multibook from client-side to server-side;
     \item Designed automated configuration logic of Bookmap Desktop and included it into the Windows installer using Java and NSIS;
    \item Implemented automated build pipeline for macOS using Gitlab CI/CD, Bash, Groovy (Gradle) and jpackage. 
 \end{itemize}
 
% \textbf{Software Engineer} \hfill Jan 2020 - June 2020\\
% Software Station \hfill \textit{Kharkiv, Ukraine}\\
% \vbox{
%     \vspace{+0.15cm}
%     \hbox{\hspace{+0.45cm}Internal mobile and web applications development using Flutter, Dart and Firebase.}
% }

\textbf{Software Engineer Intern} \hfill March 2019 -- May 2019\\
Aimprosoft \hfill \textit{Kharkiv, Ukraine}
 \begin{itemize}[topsep=2pt, itemsep=7pt,parsep=-5pt]
     \item Created Admin Dashboard using Java EE Servlets, JSP, JSTL, JDBC, Hibernate, Spring, OVal validator;
     \item Implemented from scratch some parts of Spring framework in order to apply design patterns and improve knowledge of framework.
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
    \href{https://bookmap.com/knowledgebase/docs/Addons-Multibook}{Multibook} {is a synthetic instrument that shows the consolidated state of several order books in real-time.  }
    \begin{itemize}[topsep=2pt, itemsep=7pt,parsep=-5pt]
        \item Implemented backend and GUI parts using Java, Swing and Bookmap L1 API;
        \item Created ecosystem around this project: health-check/debugging tools, automatic configuration, server-side streaming of data;
        \item Designed custom algorithm for real-time consolidation.
    \end{itemize} 
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Activities/Leadership} 
\textbf{Co-founder of university startup ``Sounce''} \hfill May 2019 -- February 2020
\begin{itemize}[topsep=2pt, itemsep=7pt,parsep=-5pt]
    \item Created MVP of mobile application, built infrastructure for data gathering and ML integration;
    \item Presented project, communicated with investors, social media, customers;
    \item Won several local competitions and got to the finals of international funding rounds as a team member.
\end{itemize} 

\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{Honors/Awards} 
\begin{itemize}
    \item Won 1st place out of 10 with a team of 3 students at IC Night Hackathon 2019 organized by Microsoft Student Partners Ukraine. In two days we prototyped a mobile application that can detect fake accounts on Instagram.
    % In two days we prototyped an application that can translate some words from the language of the deaf-and-mute into English.
    \item	Member of the finalist team at  \href{https://venturecup.dk/uswc/}{University Startup World Cup 2019} among 40 teams from all over the world. We took 4rd place out of 10 teams in Social Project section and won Social Media Award.
     \item 	Won 3rd place out of 11  with a team of 5 students at AI Hackathon 2019 conducted by local organizations. In two days we prototyped an application for deaf-and-mute language translation in real-time.
\end{itemize}



\end{rSection}

\end{document}
